---
title: "010_ABmodel_v21"
output: html_document
date: "`r Sys.Date()`"
---

# 0) Initialization

```{r setup, message=FALSE, warning=FALSE}
library(here)
library(tidyverse)
library(scales)
library(ggh4x)

# Source scripts (make sure model_functions_ingestion.R + analysis_functions_ingestion.R are updated as we did)
file_sources <- list.files(here("scripts"), pattern = "*.R$", full.names = TRUE)
invisible(lapply(file_sources, source))

th <- theme_surface_default(base_size = 9, square = TRUE)

tr <- list(
  # --- Activity metabolism ---
  a_A = 80,
  b_R = 0.78,

  # --- Oxygen supply ---
  a_O = 5,
  b_d = 0.75,
  b_v = 0.15,

  # --- Hill kinetics ---
  K_g = 2.0,
  h_g = 2.0,

  # --- Encounter ---
  a_E = 20,
  b_E = 2 / 3,

  # --- Processing ---
  a_C = 60,
  b_C = 0.75,

  # --- Maintenance ---
  alpha_M = 0.1,
  b_M = 0.75,

  # --- Intake partition fractions ---
  alpha_SDA = 0.2,
  alpha_exc = 0.1,

  # --- Temperature (Arrhenius default) ---
  T_ref = 10,
  E_M = 0.50,
  E_C = 0.50,
  E_A = 0.10,
  E_O = 0.25
)

pO2seq <- seq(0, 30, by = 0.1)
```


# 1) Test diagnostics (single mass/temperature): pO2 vs prey index

```{r}
d_test <- compute_state_surface(
  tr, masses = 1e4, Tseq = 10, pO2seq = pO2seq,
  preys = seq(0, 1, by = 0.004),
  prey_units = "prey_index",
  pair_mode = "cross", progress = TRUE
) %>%
  add_masks() %>%
  mutate(
    M_m_norm   = M_m / Cmax,
    M_act_norm = M_act / Cmax,
    D_SDA_norm = D_SDA / Cmax,
    M_exc_norm = M_exc / Cmax,
    A_assim_norm = A_assim / Cmax
  )

# Optional interpolation per plot (choose only when you want it):
#d_test_ip_E <- interp_surface(d_test, x="f_ref", y="pO2", z="E_net_norm", nx=350, ny=350) %>% add_masks()
```

```{r message=FALSE, warning=FALSE}
# Available energy
plot_surface_masked(d_test, x="f_ref", y="pO2", z="E_net_norm",
                    palette="blue", fill_title="Available energy",
                    x_limits=c(0,1), y_limits=c(0,30),
                    contours="auto",
                    theme=th) +
  labs(title="Available energy", x="prey index", y=expression("Ambient oxygen, " * p[O[2]*","*env] * " (kPa)"))

# SDA metabolism
plot_surface_masked(d_test, x="f_ref", y="pO2", z="D_SDA_norm",
                    palette="red", fill_title="SDA metabolism",
                    x_limits=c(0,1), y_limits=c(0,30),
                    contours="auto",
                    theme=th) +
  labs(title="SDA metabolism", x="prey index", y=expression("Ambient oxygen, " * p[O[2]*","*env] * " (kPa)"))

# Excretion
plot_surface_masked(d_test, x="f_ref", y="pO2", z="M_exc_norm",
                    palette="red", fill_title="Excretion",
                    x_limits=c(0,1), y_limits=c(0,30),
                    contours="auto",
                    theme=th) +
  labs(title="Excretion", x="prey index", y=expression("Ambient oxygen, " * p[O[2]*","*env] * " (kPa)"))

# Basal metabolism
plot_surface_masked(d_test, x="f_ref", y="pO2", z="M_m_norm",
                    palette="red", fill_title="Basal metabolism",
                    x_limits=c(0,1), y_limits=c(0,30),
                    contours="auto",
                    theme=th) +
  labs(title="Basal metabolism", x="prey index", y=expression("Ambient oxygen, " * p[O[2]*","*env] * " (kPa)"))

# Active metabolism
plot_surface_masked(d_test, x="f_ref", y="pO2", z="M_act_norm",
                    palette="red", fill_title="Active metabolism",
                    x_limits=c(0,1), y_limits=c(0,30),
                    contours="auto",
                    theme=th) +
  labs(title="Active metabolism", x="prey index", y=expression("Ambient oxygen, " * p[O[2]*","*env] * " (kPa)"))

# Cruising speed
plot_surface_masked(d_test, x="f_ref", y="pO2", z="U_opt",
                    palette="viridis", fill_title="U (m/s)",
                    x_limits=c(0,1), y_limits=c(0,30),
                    contours="auto",
                    theme=th) +
  labs(title="Cruising speed", x="prey index", y=expression("Ambient oxygen, " * p[O[2]*","*env] * " (kPa)"))

# f limitation
plot_surface_masked(d_test, x="f_ref", y="pO2", z="f",
                    palette="green", fill_title="f",
                    limits=c(0,1), x_limits=c(0,1), y_limits=c(0,30),
                    contours=list(
                      contour_spec(z="f", breaks=seq(0,1,0.2), linewidth=0.22, alpha=1)#,
                      #contour_spec(z="g", breaks=seq(0,1,0.2), linewidth=0.22, alpha=1, colour="black")
                    ),
                    theme=th) +
  scale_x_continuous(breaks = seq(0, 1, by = 0.2), labels = function(x) ifelse(x %in% c(0,1), as.character(as.integer(x)), sprintf("%.1f", x)),
                     limits = c(0, 1), expand = c(0, 0) ) +
  labs(title="Food limitation with f contours", x="prey index", y=expression("Ambient oxygen, " * p[O[2]*","*env] * " (kPa)"))

# g limitation
plot_surface_masked(d_test, x="f_ref", y="pO2", z="g",
                    palette="purple", fill_title="g",
                    limits=c(0,1), x_limits=c(0,1), y_limits=c(0,30),
                    contours=list(
                      #contour_spec(z="f", breaks=seq(0,1,0.2), linewidth=0.22, alpha=1),
                      contour_spec(z="g", breaks=seq(0,1,0.2), linewidth=0.22, alpha=1, colour="black")
                    ),
                    theme=th) +
  scale_x_continuous(breaks = seq(0, 1, by = 0.2), labels = function(x) ifelse(x %in% c(0,1), as.character(as.integer(x)), sprintf("%.1f", x)),
                     limits = c(0, 1), expand = c(0, 0) ) +
  labs(title="Oxygen limitation with g contours", x="prey index", y=expression("Ambient oxygen, " * p[O[2]*","*env] * " (kPa)"))

# Bivariate mix (contours toggleable)
plot_fg_bivariate(d_test, x="f_ref", y="pO2",
                  x_limits=c(0,1), y_limits=c(0,30),
                  contour_fg_mult=FALSE, theme=th) +
  scale_x_continuous(breaks = seq(0, 1, by = 0.2), labels = function(x) ifelse(x %in% c(0,1), as.character(as.integer(x)), sprintf("%.1f", x)),
                     limits = c(0, 1), expand = c(0, 0) ) +
  labs(title="Bivariate limitation mix", x="prey index", y=expression("Ambient oxygen, " * p[O[2]*","*env] * " (kPa)"))

# pO2 interior
plot_surface_masked(d_test, x="f_ref", y="pO2", z="pO2_int",
                    palette="purple", fill_title="Interior oxygen",
                    x_limits=c(0,1), y_limits=c(0,30),
                    contours=contour_spec(z="pO2_int", breaks=seq(0,30,5), linewidth=0.22, alpha=1),
                    theme=th) +
  labs(title="Interior oxygen", x="prey index", y=expression("Ambient oxygen, " * p[O[2]*","*env] * " (kPa)"))

# Prey density
d_test2 <- d_test %>%
  dplyr::mutate(
    B_used_pos = dplyr::if_else(B_used <= 0 | !is.finite(B_used), NA_real_, B_used),
    logB = log10(B_used_pos)
  )
plot_surface_masked(d_test2, x="f_ref", y="pO2", z="logB",
                    palette="green",
                    fill_title=expression(log[10]*"(Prey biomass)"),
                    x_limits=c(0,1), y_limits=c(0,30),
                    limits = c(0, 4),   # <- log10 limits
                    contours=contour_spec(z="logB", breaks=c(1e0,1e1,1e2,1e3,1e4), linewidth=0.22, alpha=1),
                    theme=th) +
  labs(title="Prey density", x="prey index", y=expression("Ambient oxygen, " * p[O[2]*","*env] * " (kPa)"))
```


# 2) pO2 vs prey density (four separate 4-panel plots)

```{r}
d_prey <- compute_state_surface(
  tr, masses=c(1e1,1e5), Tseq=c(5,25), pO2seq=pO2seq,
  preys=seq(0,1,length.out=220), prey_units="prey_index",
  pair_mode="cross", progress=TRUE
) %>%
  add_masks() %>%
  mutate(
    mass_lab=factor(mass, levels=c(1e1,1e5), labels=c("m = 1e0 g","m = 1e4 g")),
    T_lab=factor(T, levels=c(5,25), labels=c("T = 5°C","T = 25°C"))
  )
```

```{r message=FALSE, warning=FALSE}
# Available energy
plot_surface_masked(d_prey, x="f_ref", y="pO2", z="E_net_norm",
                    palette="blue", fill_title="E/Cmax",
                    x_limits=c(0,1), y_limits=c(0,30),
                    contours="auto", theme=th) +
  facet_grid2(rows=vars(T_lab), cols=vars(mass_lab)) +
  scale_x_continuous(breaks = seq(0, 1, by = 0.2), labels = function(x) ifelse(x %in% c(0,1), as.character(as.integer(x)), sprintf("%.1f", x)),
                     limits = c(0, 1), expand = c(0, 0) ) +
  labs(title="Available energy", x="prey index", y=expression("Ambient oxygen, " * p[O[2]*","*env] * " (kPa)"))

# Cruising speed
plot_surface_masked(d_prey, x="f_ref", y="pO2", z="U_opt",
                    palette="viridis", fill_title="U (m/s)",
                    x_limits=c(0,1), y_limits=c(0,30),
                    contours="auto",
                    theme=th) +
  facet_grid2(rows=vars(T_lab), cols=vars(mass_lab)) +
  labs(title="Available energy", x="prey index", y=expression("Ambient oxygen, " * p[O[2]*","*env] * " (kPa)"))

# Bivariate limitation
plot_fg_bivariate(d_prey, x="f_ref", y="pO2",
                  x_limits=c(0,1), y_limits=c(0,30),
                  contour_fg_mult=FALSE, theme=th) +
  facet_grid2(rows=vars(T_lab), cols=vars(mass_lab)) +
  labs(title="Bivariate limitation mix", x="prey index", y=expression("Ambient oxygen, " * p[O[2]*","*env] * " (kPa)"))
```

```{r message=FALSE, warning=FALSE}
d_prey <- d_prey %>%
  mutate(
    # Total aerobic metabolic demand (respired components)
    M_tot_aero = M_m + M_act + D_SDA,

    # Effective MI using realized supply (dimensionless)
    MI_eff = if_else(is.finite(O2_supply) & is.finite(M_tot_aero) & M_tot_aero > 0,
                     O2_supply / M_tot_aero, NA_real_),

    # Optional: MI analogue using environmental pO2 (estimate kO from the run)
    kO_est = if_else(is.finite(O2_supply) & is.finite(pO2) & is.finite(pO2_int) & (pO2 > pO2_int),
                     O2_supply / (pO2 - pO2_int), NA_real_),
    MI_env = if_else(is.finite(kO_est) & is.finite(M_tot_aero) & M_tot_aero > 0,
                     kO_est * pO2 / M_tot_aero, NA_real_),

    # FAL = total aerobic / basal
    FAL = if_else(is.finite(M_m) & M_m > 0 & is.finite(M_tot_aero),
                  M_tot_aero / M_m, NA_real_)
  )

# MI_env surface
plot_surface_masked(d_prey, x="f_ref", y="pO2", z="MI_env",
                    palette="red", fill_title="MI_env (O2_supply / demand)",
                    x_limits=c(0,1), y_limits=c(0,30),
                    contours=contour_spec(z="MI_env", breaks=c(1, 2, 3, 4, 5, 6, 7, 8), linewidth=0.22, alpha=1),
                    theme=th) +
  facet_grid2(rows=vars(T_lab), cols=vars(mass_lab)) +
  scale_x_continuous(breaks=seq(0,1,0.2), labels=function(x) ifelse(x %in% c(0,1), as.character(as.integer(x)), sprintf("%.1f", x)),
                     limits=c(0,1), expand=c(0,0)) +
  labs(title="Effective metabolic index", x="prey index", y=expression("Ambient oxygen, " * p[O[2]*","*env] * " (kPa)"))

# FAL surface
plot_surface_masked(d_prey, x="f_ref", y="pO2", z="FAL",
                    palette="red", fill_title="FAL = (Mm+Ma+SDA)/Mm",
                    x_limits=c(0,1), y_limits=c(0,30),
                    contours=contour_spec(z="FAL", breaks=c(1.5, 2, 2.5, 3), linewidth=0.22, alpha=1), 
                    theme=th) +
  facet_grid2(rows=vars(T_lab), cols=vars(mass_lab)) +
  scale_x_continuous(breaks=seq(0,1,0.2), labels=function(x) ifelse(x %in% c(0,1), as.character(as.integer(x)), sprintf("%.1f", x)),
                     limits=c(0,1), expand=c(0,0)) +
  labs(title="Factorial aerobic load", x="prey index", y=expression("Ambient oxygen, " * p[O[2]*","*env] * " (kPa)"))
```


# 3) Feeding level: pO2 vs temperature (four separate 4-panel plots)

```{r}
d_temp_fl <- compute_state_surface(
  tr, masses=c(1e1,1e5), Tseq=seq(0,30,by=0.25), pO2seq=pO2seq,
  preys=c(0.9,0.6), prey_units="feeding_level",
  pair_mode="cross", progress=TRUE
) %>%
  add_masks() %>%
  mutate(
    mass_lab=factor(mass, levels=c(1e1,1e5), labels=c("m = 1e0 g","m = 1e4 g")),
    f_lab=factor(f_ref, levels=c(0.9,0.6), labels=c("feeding level = 0.9","feeding level = 0.6"))
  )
```

```{r message=FALSE, warning=FALSE}
# Available energy
plot_surface_masked(d_temp_fl, x="T", y="pO2", z="E_net_norm",
                    palette="blue", fill_title="E/Cmax",
                    x_limits=c(0,30), y_limits=c(0,30),
                    contours=list( #contours="auto",
                      contour_spec(z="E_net_norm", breaks=seq(0,1,0.1), linewidth=0.22, alpha=1)
                    ),
                    theme=th) +
  facet_grid2(rows=vars(f_lab), cols=vars(mass_lab)) +
  labs(title="Available energy", x="Temperature, T (°C)", y=expression("Ambient oxygen, " * p[O[2]*","*env] * " (kPa)"))

# Cruising speed
plot_surface_masked(d_temp_fl, x="T", y="pO2", z="U_opt",
                    palette="viridis", fill_title="U (m/s)",
                    x_limits=c(0,30), y_limits=c(0,30),
                    contours="auto",
                    theme=th) +
  facet_grid2(rows=vars(f_lab), cols=vars(mass_lab)) +
  labs(title="Available energy", x="Temperature, T (°C)", y=expression("Ambient oxygen, " * p[O[2]*","*env] * " (kPa)"))

# Bivariate limitation
plot_fg_bivariate(d_temp_fl, x="T", y="pO2",
                  x_limits=c(0,30), y_limits=c(0,30),
                  contour_fg_mult=TRUE, theme=th) +
  facet_grid2(rows=vars(f_lab), cols=vars(mass_lab)) +
  labs(title="Bivariate limitation mix", x="Temperature, T (°C)", y=expression("Ambient oxygen, " * p[O[2]*","*env] * " (kPa)"))
```


# 4) Prey index: pO2 vs temperature (four separate 4-panel plots)

```{r}
d_temp_fl <- compute_state_surface(
  tr, masses=c(1e1,1e5), Tseq=seq(0,30,by=0.25), pO2seq=pO2seq,
  preys=c(0.9,0.6), prey_units="prey_index",
  D=2,
  pair_mode="cross", progress=TRUE
) %>%
  add_masks() %>%
  mutate(
    mass_lab=factor(mass, levels=c(1e1,1e5), labels=c("m = 1e0 g","m = 1e4 g")),
    f_lab=factor(f_ref, levels=c(0.9,0.6), labels=c("prey index = 0.9","prey index = 0.6"))
  )
```

```{r message=FALSE, warning=FALSE}
# Available energy
plot_surface_masked(d_temp_fl, x="T", y="pO2", z="E_net_norm",
                    palette="blue", fill_title="E/Cmax",
                    x_limits=c(0,30), y_limits=c(0,30),
                    contours=list( #contours="auto",
                      contour_spec(z="E_net_norm", breaks=seq(0,1,0.1), linewidth=0.22, alpha=1)
                    ),
                    theme=th) +
  facet_grid2(rows=vars(f_lab), cols=vars(mass_lab)) +
  labs(title="Available energy", x="Temperature, T (°C)", y=expression("Ambient oxygen, " * p[O[2]*","*env] * " (kPa)"))

# Cruising speed
plot_surface_masked(d_temp_fl, x="T", y="pO2", z="U_opt",
                    palette="viridis", fill_title="U (m/s)",
                    x_limits=c(0,30), y_limits=c(0,30),
                    contours="auto",
                    theme=th) +
  facet_grid2(rows=vars(f_lab), cols=vars(mass_lab)) +
  labs(title="Available energy", x="Temperature, T (°C)", y=expression("Ambient oxygen, " * p[O[2]*","*env] * " (kPa)"))

# Bivariate limitation
plot_fg_bivariate(d_temp_fl, x="T", y="pO2",
                  x_limits=c(0,30), y_limits=c(0,30),
                  contour_fg_mult=TRUE, theme=th) +
  facet_grid2(rows=vars(f_lab), cols=vars(mass_lab)) +
  labs(title="Bivariate limitation mix", x="Temperature, T (°C)", y=expression("Ambient oxygen, " * p[O[2]*","*env] * " (kPa)"))
```


# 5) Metabolic allocation (stacked; explicit excretion)

```{r metabolic-allocation}
mass_seq <- 10^seq(-3, 5, length.out = 120)
scen <- tribble(
  ~scenario, ~T, ~pO2, ~f_ref,
  "Baseline", 10, 25, 0.75,
  "Hyperthermic", 25, 25, 0.75,
  "Hypoxic", 10, 10, 0.75,
  "Oligotrophic", 10, 25, 0.50
)

alloc_state <- purrr::pmap_dfr(scen, function(scenario, T, pO2, f_ref) {
  B_vec <- B_from_f(f_ref = rep(f_ref, length(mass_seq)), w = mass_seq, tr = tr,
                    T_ref = rep(10, length(mass_seq)), pO2_ref = rep(25, length(mass_seq)),
                    U_lo = 1e-5, U_mech = 5, enforce_O2_feasible = TRUE)
  purrr::map2_dfr(mass_seq, B_vec, function(m, B) {
    st <- find_U_opt(pO2_env = pO2, T = T, w = m, prey = B, tr = tr, U_lo = 1e-5, U_mech = 5)
    tibble(
      scenario = scenario,
      mass = m,
      Cmax = st$Cmax,
      f = st$f,
      g = st$g,
      U = st$U_opt,
      `Basal metabolism` = st$M_m,
      `Active metabolism` = st$M_act,
      SDA = st$D_SDA,
      Excretion = st$M_exc,
      `Available energy` = st$E_net
    )
  })
})

alloc_long <- alloc_state %>%
  pivot_longer(cols = c("Basal metabolism", "Active metabolism", "SDA", "Excretion", "Available energy"),
               names_to = "Process", values_to = "value") %>%
  mutate(value_norm = value / Cmax,
         Process = factor(Process, levels = c("Basal metabolism", "Active metabolism", "SDA", "Excretion", "Available energy")))

alloc_cols <- c("Basal metabolism"="#440154", "Active metabolism"="#8a5796", "SDA"="#e0bce8", "Excretion"="gray90", "Available energy"="#67A5CA")

ggplot(alloc_long, aes(x = mass, y = value_norm, fill = Process)) +
  geom_area(position = "stack", color = "gray50", linewidth = 0.25) +
  scale_y_continuous(limits = c(0,1), expand = c(0, 0)) +
    scale_x_log10(
    breaks = 10^c(-2, 0, 2, 4),
    labels = label_10pow(),
    expand = c(0, 0)
  ) +
  scale_fill_manual(values = alloc_cols) +
  facet_wrap(~scenario, nrow = 1) +
  labs(x = "Body mass, w (g)", y = "Allocation / Cmax", title = "Metabolic allocation") +
  th

alloc_state %>%
  mutate(fg = f * g) %>%
  select(scenario, mass, f, g, fg) %>%
  pivot_longer(cols = c(f, g, fg), names_to = "limiter", values_to = "value") %>%
  mutate(limiter = factor(limiter, levels = c("g", "f", "fg"))) %>%
  ggplot(aes(x = mass, y = value, colour = limiter)) +
  geom_line(linewidth = 0.8) +
  scale_color_manual(values = c(g = "#6a51a3", f = "#238b45", fg = "black")) +
  scale_x_log10(
    breaks = 10^c(-2, 0, 2, 4),
    labels = label_10pow(),
    expand = c(0, 0)
  ) +
  scale_y_continuous(limits = c(0, 1), expand = c(0, 0)) +
  facet_wrap(~scenario, nrow = 1) +
  labs(x = "Body mass, w (g)", y = "Limitation", colour = NULL,
       title = "f, g, and f·g across size (aligned by scenario)") +
  th

alloc_state %>%
  select(scenario, mass, U) %>%
  pivot_longer(cols = c(U), names_to = "limiter", values_to = "value") %>%
  mutate(limiter = factor(limiter, levels = c("U"))) %>%
  ggplot(aes(x = mass, y = value, colour = limiter)) +
  geom_line(linewidth = 0.8) +
  scale_color_manual(values = c(U = "black")) +
  scale_x_log10(
    breaks = 10^c(-2, 0, 2, 4),
    labels = label_10pow(),
    expand = c(0, 0)
  ) +
  scale_y_log10(expand = c(0, 0)) +
  facet_wrap(~scenario, nrow = 1) +
  labs(x = "Body mass, w (g)", y = "U", colour = NULL,
       title = "Cruising speed across size (aligned by scenario)") +
  th

U_scaling <- alloc_state %>%
  filter(is.finite(U), U > 0, is.finite(mass), mass > 0) %>%
  group_by(scenario) %>%
  summarise(
    n = n(),
    beta = coef(lm(log10(U) ~ log10(mass)))[["log10(mass)"]],
    alpha = coef(lm(log10(U) ~ log10(mass)))[["(Intercept)"]],
    r2 = summary(lm(log10(U) ~ log10(mass)))$r.squared,
    .groups = "drop"
  ) %>%
  mutate(
    # U = A * m^beta
    A = 10^alpha
  )

U_scaling

Mact_scaling <- alloc_state %>%
  dplyr::filter(is.finite(`Active metabolism`), `Active metabolism` > 0,
                is.finite(mass), mass > 0) %>%
  dplyr::group_by(scenario) %>%
  dplyr::summarise(
    n = dplyr::n(),
    beta  = coef(stats::lm(log10(`Active metabolism`) ~ log10(mass)))[["log10(mass)"]],
    alpha = coef(stats::lm(log10(`Active metabolism`) ~ log10(mass)))[["(Intercept)"]],
    r2 = summary(stats::lm(log10(`Active metabolism`) ~ log10(mass)))$r.squared,
    .groups = "drop"
  ) %>%
  dplyr::mutate(A = 10^alpha)  # so M_act = A * m^beta

Mact_scaling

# Total "metabolism" scaling (as you defined it): M_total = Excretion + SDA + Basal + Active
Mtot_scaling <- alloc_state %>%
  dplyr::mutate(
    M_total = Excretion + SDA + `Basal metabolism` + `Active metabolism`
  ) %>%
  dplyr::filter(is.finite(M_total), M_total > 0,
                is.finite(mass), mass > 0) %>%
  dplyr::group_by(scenario) %>%
  dplyr::summarise(
    n = dplyr::n(),
    beta  = coef(stats::lm(log10(M_total) ~ log10(mass)))[["log10(mass)"]],
    alpha = coef(stats::lm(log10(M_total) ~ log10(mass)))[["(Intercept)"]],
    r2 = summary(stats::lm(log10(M_total) ~ log10(mass)))$r.squared,
    .groups = "drop"
  ) %>%
  dplyr::mutate(A = 10^alpha)  # so M_total = A * m^beta

Mtot_scaling
```

```{r metabolic-allocation-2, warning=FALSE}
mass_seq <- 10^seq(-3, 5, length.out = 120)
scen <- tribble(
  ~scenario, ~T, ~pO2, ~f_ref,
  #"Baseline", 10, 25, 0.75,
  "Hyperthermic + Hypoxic", 25, 10, 0.75,
  "Hypoxic + Oligotrophic", 10, 10, 0.50,
  "Oligotrophic + Hyperthermic", 25, 25, 0.50,
  "Oligotrophic + Hyperthermic + \nHypoxic", 25, 10, 0.50
)

alloc_state <- purrr::pmap_dfr(scen, function(scenario, T, pO2, f_ref) {
  B_vec <- B_from_f(f_ref = rep(f_ref, length(mass_seq)), w = mass_seq, tr = tr,
                    T_ref = rep(10, length(mass_seq)), pO2_ref = rep(25, length(mass_seq)),
                    U_lo = 1e-5, U_mech = 5, enforce_O2_feasible = TRUE)
  purrr::map2_dfr(mass_seq, B_vec, function(m, B) {
    st <- find_U_opt(pO2_env = pO2, T = T, w = m, prey = B, tr = tr, U_lo = 1e-5, U_mech = 5)
    tibble(
      scenario = scenario,
      mass = m,
      Cmax = st$Cmax,
      f = st$f,
      g = st$g,
      U = st$U_opt,
      `Basal metabolism` = st$M_m,
      `Active metabolism` = st$M_act,
      SDA = st$D_SDA,
      Excretion = st$M_exc,
      `Available energy` = st$E_net
    )
  })
})

alloc_long <- alloc_state %>%
  pivot_longer(cols = c("Basal metabolism", "Active metabolism", "SDA", "Excretion", "Available energy"),
               names_to = "Process", values_to = "value") %>%
  mutate(value_norm = value / Cmax,
         Process = factor(Process, levels = c("Basal metabolism", "Active metabolism", "SDA", "Excretion", "Available energy")))

alloc_cols <- c("Basal metabolism"="#440154", "Active metabolism"="#8a5796", "SDA"="#e0bce8", "Excretion"="gray90", "Available energy"="#67A5CA")

ggplot(alloc_long, aes(x = mass, y = value_norm, fill = Process)) +
  geom_area(position = "stack", color = "gray50", linewidth = 0.25) +
  scale_y_continuous(limits = c(0,1), expand = c(0, 0)) +
    scale_x_log10(
    breaks = 10^c(-2, 0, 2, 4),
    labels = label_10pow(),
    expand = c(0, 0)
  ) +
  scale_fill_manual(values = alloc_cols) +
  facet_wrap(~scenario, nrow = 1) +
  labs(x = "Body mass, w (g)", y = "Allocation / Cmax", title = "Metabolic allocation") +
  th

alloc_state %>%
  mutate(fg = f * g) %>%
  select(scenario, mass, f, g, fg) %>%
  pivot_longer(cols = c(f, g, fg), names_to = "limiter", values_to = "value") %>%
  mutate(limiter = factor(limiter, levels = c("g", "f", "fg"))) %>%
  ggplot(aes(x = mass, y = value, colour = limiter)) +
  geom_line(linewidth = 0.8) +
  scale_color_manual(values = c(g = "#6a51a3", f = "#238b45", fg = "black")) +
  scale_x_log10(
    breaks = 10^c(-2, 0, 2, 4),
    labels = label_10pow(),
    expand = c(0, 0)
  ) +
  scale_y_continuous(limits = c(0, 1), expand = c(0, 0)) +
  facet_wrap(~scenario, nrow = 1) +
  labs(x = "Body mass, w (g)", y = "Limitation", colour = NULL,
       title = "f, g, and f·g across size (aligned by scenario)") +
  th

U_scaling <- alloc_state %>%
  filter(is.finite(U), U > 0, is.finite(mass), mass > 0) %>%
  group_by(scenario) %>%
  summarise(
    n = n(),
    beta = coef(lm(log10(U) ~ log10(mass)))[["log10(mass)"]],
    alpha = coef(lm(log10(U) ~ log10(mass)))[["(Intercept)"]],
    r2 = summary(lm(log10(U) ~ log10(mass)))$r.squared,
    .groups = "drop"
  ) %>%
  mutate(
    # U = A * m^beta
    A = 10^alpha
  )

U_scaling

Mact_scaling <- alloc_state %>%
  dplyr::filter(is.finite(`Active metabolism`), `Active metabolism` > 0,
                is.finite(mass), mass > 0) %>%
  dplyr::group_by(scenario) %>%
  dplyr::summarise(
    n = dplyr::n(),
    beta  = coef(stats::lm(log10(`Active metabolism`) ~ log10(mass)))[["log10(mass)"]],
    alpha = coef(stats::lm(log10(`Active metabolism`) ~ log10(mass)))[["(Intercept)"]],
    r2 = summary(stats::lm(log10(`Active metabolism`) ~ log10(mass)))$r.squared,
    .groups = "drop"
  ) %>%
  dplyr::mutate(A = 10^alpha)  # so M_act = A * m^beta

Mact_scaling

# Total "metabolism" scaling (as you defined it): M_total = Excretion + SDA + Basal + Active
Mtot_scaling <- alloc_state %>%
  dplyr::mutate(
    M_total = Excretion + SDA + `Basal metabolism` + `Active metabolism`
  ) %>%
  dplyr::filter(is.finite(M_total), M_total > 0,
                is.finite(mass), mass > 0) %>%
  dplyr::group_by(scenario) %>%
  dplyr::summarise(
    n = dplyr::n(),
    beta  = coef(stats::lm(log10(M_total) ~ log10(mass)))[["log10(mass)"]],
    alpha = coef(stats::lm(log10(M_total) ~ log10(mass)))[["(Intercept)"]],
    r2 = summary(stats::lm(log10(M_total) ~ log10(mass)))$r.squared,
    .groups = "drop"
  ) %>%
  dplyr::mutate(A = 10^alpha)  # so M_total = A * m^beta

Mtot_scaling
```

# 6) E_avail over temperature: prey index vs feeding level

```{r message=FALSE, warning=FALSE}
T_seq <- seq(0, 30, by = 0.25)
fixed_prey_index <- 0.75
fixed_feeding_level <- 0.75
show_U <- FALSE

# Keep: prey index at 25 & 10 kPa; feeding level at 25 kPa only
scenario_grid <- tidyr::crossing(
  mass = c(1e1, 1e5),
  mode = c("Fixed prey index", "Fixed feeding level"),
  pO2 = c(25, 10)
) %>%
  dplyr::filter(!(mode == "Fixed feeding level" & pO2 == 10)) %>%
  dplyr::mutate(
    mass_lab = factor(mass, levels = c(1e1, 1e5), labels = c("m = 1e0 g", "m = 1e4 g")),
    mode = factor(mode, levels = c("Fixed prey index", "Fixed feeding level")),
    pO2_lab = factor(pO2, levels = c(25, 10), labels = c("25 kPa", "10 kPa"))
  )

temp_series <- purrr::pmap_dfr(scenario_grid, function(mass, mode, pO2, mass_lab, pO2_lab) {
  d <- if (mode == "Fixed prey index") {
    compute_state_surface(
      tr, masses = mass, Tseq = T_seq, pO2seq = pO2,
      preys = fixed_prey_index, prey_units = "prey_index",
      pair_mode = "cross", progress = FALSE
    )
  } else {
    compute_state_surface(
      tr, masses = mass, Tseq = T_seq, pO2seq = pO2,
      preys = fixed_feeding_level, prey_units = "feeding_level",
      pair_mode = "cross", progress = FALSE
    )
  }

  dplyr::mutate(d, mode = mode, pO2 = pO2, pO2_lab = pO2_lab, mass_lab = mass_lab)
})

# ------------------------------ Plot 1: E_avail (all blue; style encodes scenario) ------------------------------
mode_lw <- c("Fixed prey index" = 0.75, "Fixed feeding level" = 1.5)
pO2_ltys  <- c("25 kPa" = "solid", "10 kPa" = "22")  # one simple dashed pattern

# IMPORTANT: make sure mode is a factor with these levels, same as Plot 2
temp_series <- temp_series %>%
  dplyr::mutate(
    mode = factor(mode, levels = c("Fixed prey index", "Fixed feeding level")),
    pO2_lab = factor(pO2_lab, levels = c("25 kPa", "10 kPa"))
  )

ggplot(temp_series, aes(x = T, y = E_net_norm)) +
  geom_line(aes(linetype = pO2_lab, linewidth = mode), colour = "#67A5CA") +
  scale_linetype_manual(values = pO2_ltys) +
  scale_linewidth_manual(values = mode_lw) +
  facet_wrap(~mass_lab, nrow = 1) +
  scale_x_continuous(breaks = c(0,10,20,30), expand = c(0, 0)) +
  scale_y_continuous(limits = c(0, 0.5), expand = c(0, 0)) +
  labs(
    x = "Temperature, T (°C)",
    y = "E_avail / Cmax",
    linetype = "Oxygen",
    linewidth = NULL,
    title = "Available energy over temperature",
    subtitle = paste0("Fixed prey index = ", fixed_prey_index,
                      ", fixed feeding level = ", fixed_feeding_level,
                      " (feeding level shown only at 25 kPa)")
  ) +
  th

# ------------------------------ Plot 2: f and g ------------------------------
metric_cols <- c(f = "#238b45", g = "#6a51a3", U_opt = "#ff8c00")
metrics_to_plot <- c("f", "g")
if (isTRUE(show_U)) metrics_to_plot <- c(metrics_to_plot, "U_opt")

# Encode:
# - color = metric (f vs g)
# - linetype = oxygen (25 vs 10 kPa)
# - linewidth = mode (prey index thicker, feeding level thinner)

temp_series %>%
  dplyr::select(T, mass_lab, mode, pO2_lab, all_of(metrics_to_plot)) %>%
  tidyr::pivot_longer(cols = all_of(metrics_to_plot), names_to = "metric", values_to = "value") %>%
  dplyr::mutate(
    metric = factor(metric, levels = c("f", "g", "U_opt")),
    mode = factor(mode, levels = c("Fixed prey index", "Fixed feeding level"))
  ) %>%
  ggplot(aes(x = T, y = value)) +
  geom_line(aes(colour = metric, linetype = pO2_lab, linewidth = mode)) +
  scale_color_manual(values = metric_cols[names(metric_cols) %in% metrics_to_plot]) +
  scale_linetype_manual(values = pO2_ltys) +
  scale_linewidth_manual(values = mode_lw) +
  facet_wrap(~mass_lab, nrow = 1) +
  scale_x_continuous(breaks = c(0,10,20,30), expand = c(0, 0)) +
  scale_y_continuous(breaks=c(0.0, 0.2, 0.4, 0.6, 0.8, 1.0), limits = c(0, 1), expand = c(0, 0)) +
  labs(
    x = "Temperature, T (°C)", y = "Value",
    colour = NULL, linetype = "Oxygen", linewidth = NULL,
    title = "f and g over temperature",
    subtitle = "Colour = metric (f green, g purple); linetype = oxygen; thickness = mode"
  ) +
  th
```

# 7) U over prey index

```{r}
prey_seq <- seq(0, 1, by = 0.002)

scenario_grid <- tidyr::crossing(
  scenario = c("Baseline", "Hyperthermic", "Hypoxic"),
  mass = c(1e1, 1e5)
) %>%
  dplyr::mutate(
    mass_lab = factor(mass, levels = c(1e1, 1e5), labels = c("m = 1e0 g", "m = 1e4 g")),
    lw = dplyr::if_else(mass == 1e0, 0.75, 1.5),
    T = dplyr::case_when(
      scenario == "Baseline" ~ 10,
      scenario == "Hyperthermic" ~ 30,
      scenario == "Hypoxic" ~ 10
    ),
    pO2 = dplyr::case_when(
      scenario == "Baseline" ~ 25,
      scenario == "Hyperthermic" ~ 25,
      scenario == "Hypoxic" ~ 10
    )
  )

U_series <- purrr::pmap_dfr(scenario_grid, function(scenario, mass, mass_lab, lw, T, pO2) {

  d <- compute_state_surface(
    tr,
    masses = mass,
    Tseq = T,
    pO2seq = pO2,
    preys = prey_seq,
    prey_units = "prey_index",
    pair_mode = "cross",
    progress = TRUE
  )

  d <- d %>%
    dplyr::mutate(
      scenario = scenario,
      mass_lab = mass_lab,
      lw = lw,
      # solid if E_avail > 0 and finite; dashed otherwise
      E_ok = is.finite(E_net) & (E_net > 0),
      lty = dplyr::if_else(E_ok, "Positive E_avail", "Negative/NA E_avail")
    ) %>%
    dplyr::arrange(f_ref)

  # Split into contiguous segments of constant linetype, per scenario x mass
  d <- d %>%
    dplyr::mutate(seg_id = cumsum(dplyr::coalesce(lty != dplyr::lag(lty), TRUE)))

  d
})
```

```{r}
sc_cols <- c(
  "Baseline" = "gray60",
  "Hyperthermic" = "#B2182B",
  "Hypoxic" = "#8A5796"
)

ggplot(U_series, aes(x = f_ref, y = U_opt)) +
  geom_line(
    aes(colour = scenario, linetype = lty, group = interaction(scenario, mass_lab, seg_id), linewidth = lw)
  ) +
  scale_color_manual(values = sc_cols) +
  scale_linetype_manual(values = c("Positive E_avail" = "solid", "Negative/NA E_avail" = "22")) +
  scale_linewidth_identity(guide = "none") +
  scale_x_continuous(
    expand = c(0, 0),
    breaks = seq(0, 1, by = 0.2),
    labels = function(x) ifelse(x %in% c(0,1), as.character(as.integer(x)), sprintf("%.1f", x))
  ) +
  scale_y_continuous(expand = c(0, 0)) +
  labs(
    x = "prey index",
    y = expression(U^"*"),
    colour = NULL,
    linetype = NULL,
    #title = expression("Cruising speed " * U^"* * " over prey index"),
    #subtitle = "Colour = scenario; thickness = mass (thin 1e0g, thick 1e4g); dashed where E_avail ≤ 0 or NA"
  ) +
  th
```


# 8) Minimum pO2 mass-scaling analysis

```{r}
find_zero_crossing <- function(x, y) {
  ok <- is.finite(x) & is.finite(y)
  x <- x[ok]; y <- y[ok]
  if (length(x) < 2) return(NA_real_)

  o <- order(x)
  x <- x[o]; y <- y[o]

  # exact zero
  iz <- which(y == 0)
  if (length(iz) > 0) return(x[min(iz)])

  s <- sign(y)
  idx <- which(s[-length(s)] * s[-1] < 0)
  if (length(idx) == 0) return(NA_real_)

  i <- idx[1]
  x1 <- x[i]; x2 <- x[i+1]
  y1 <- y[i]; y2 <- y[i+1]
  x1 + (0 - y1) * (x2 - x1) / (y2 - y1)
}
```

```{r}
mass_seq <- 10^seq(0, 6, by = 1)   # 1e0 to 1e6
pO2_seq  <- seq(0, 30, by = 0.1)

f_ref_use <- 0.75   # prey index OR feeding level target

d_slice <- compute_state_surface(
  tr,
  masses = mass_seq,
  Tseq   = 10,
  pO2seq = pO2_seq,
  preys  = f_ref_use,
  prey_units = "prey_index",   # or "feeding_level"
  pair_mode = "cross",
  progress = TRUE
)
```

```{r}
thr_mass <- d_slice %>%
  mutate(
    SD_margin = O2_supply - O2_demand
  ) %>%
  group_by(mass) %>%
  summarise(
    pO2_E0 = find_zero_crossing(pO2, E_net),
    pO2_SD = find_zero_crossing(pO2, SD_margin),
    .groups = "drop"
  ) %>%
  mutate(
    # keep copies in log space for fits/plots if useful
    logm = log10(mass),
    log_pO2_E0 = if_else(is.finite(pO2_E0) & pO2_E0 > 0, log10(pO2_E0), NA_real_),
    log_pO2_SD = if_else(is.finite(pO2_SD) & pO2_SD > 0, log10(pO2_SD), NA_real_)
  )

thr_mass
```

```{r}
thr_long <- thr_mass %>%
  pivot_longer(cols = c(pO2_E0, pO2_SD),
               names_to = "threshold", values_to = "pO2_thr") %>%
  mutate(threshold = recode(threshold,
                            pO2_E0 = "E_net = 0",
                            pO2_SD = "O2 supply = demand"))

ggplot(thr_long, aes(x = mass, y = pO2_thr, colour = threshold)) +
  geom_line(linewidth = 0.9, na.rm = TRUE) +
  geom_point(size = 1.6, na.rm = TRUE) +
  scale_x_log10(breaks = 10^(0:6), labels = label_10pow(), expand = c(0, 0)) +
  scale_y_continuous(breaks = c(0,10,20,30), limits = c(0, 30), expand = c(0, 0)) +
  labs(x = "Body mass, w (g)", y = expression(p[O[2]]~"threshold (kPa)"),
       colour = NULL,
       title = "pO2 thresholds vs mass at 10°C",
       subtitle = paste0("Prey setting: ", f_ref_use, " (", "prey_units = prey_index", ")")) +
  th
```

```{r}
# Fit: log10(pO2_thr) ~ alpha + beta*log10(mass)
fit_scaling <- function(df, ycol) {
  d <- df %>%
    filter(is.finite(.data[[ycol]]), .data[[ycol]] > 0, is.finite(mass), mass > 0) %>%
    mutate(logy = log10(.data[[ycol]]), logm = log10(mass))

  if (nrow(d) < 3) return(tibble(n = nrow(d), alpha = NA_real_, beta = NA_real_, r2 = NA_real_, A = NA_real_))

  fit <- lm(logy ~ logm, data = d)
  co <- coef(fit)
  tibble(
    n = nrow(d),
    alpha = unname(co[1]),
    beta  = unname(co[2]),
    r2 = summary(fit)$r.squared,
    A = 10^unname(co[1])
  )
}

scaling_E0 <- fit_scaling(thr_mass, "pO2_E0") %>% mutate(threshold = "E_net = 0")
scaling_SD <- fit_scaling(thr_mass, "pO2_SD") %>% mutate(threshold = "O2 supply = demand")

bind_rows(scaling_E0, scaling_SD)
```


# 9) Requested update: 8-scenario metabolic allocation with f and g

```{r metabolic-allocation-8panel, warning=FALSE}
scenario_order <- c(
  "Baseline", "Oligotrophic", "Hyperthermic", "Hypoxic",
  "Oligotrophic+Hyperthermic", "Oligotrophic+Hypoxic",
  "Hyperthermic+Hypoxic", "Hyperthermic+Hypoxic+Oligotrophic"
)

scen_all <- tribble(
  ~scenario, ~T, ~pO2, ~f_ref,
  "Baseline", 10, 25, 0.75,
  "Oligotrophic", 10, 25, 0.50,
  "Hyperthermic", 25, 25, 0.75,
  "Hypoxic", 10, 10, 0.75,
  "Oligotrophic+Hyperthermic", 25, 25, 0.50,
  "Oligotrophic+Hypoxic", 10, 10, 0.50,
  "Hyperthermic+Hypoxic", 25, 10, 0.75,
  "Hyperthermic+Hypoxic+Oligotrophic", 25, 10, 0.50
)

mass_seq <- 10^seq(-3, 5, length.out = 120)
alloc8 <- purrr::pmap_dfr(scen_all, function(scenario, T, pO2, f_ref) {
  B_vec <- B_from_f(f_ref = rep(f_ref, length(mass_seq)), w = mass_seq, tr = tr,
                    T_ref = rep(10, length(mass_seq)), pO2_ref = rep(25, length(mass_seq)),
                    U_lo = 1e-5, U_mech = 5, enforce_O2_feasible = TRUE)
  purrr::map2_dfr(mass_seq, B_vec, function(m, B) {
    st <- find_U_opt(pO2_env = pO2, T = T, w = m, prey = B, tr = tr, U_lo = 1e-5, U_mech = 5)
    tibble(
      scenario = scenario, mass = m, Cmax = st$Cmax,
      f = st$f, g = st$g,
      `Basal metabolism` = st$M_m / st$Cmax,
      `Active metabolism` = st$M_act / st$Cmax,
      SDA = st$D_SDA / st$Cmax,
      Excretion = st$M_exc / st$Cmax,
      `Available energy` = st$E_net / st$Cmax
    )
  })
}) %>% mutate(scenario = factor(scenario, levels = scenario_order))

alloc_long8 <- alloc8 %>%
  pivot_longer(cols = c("Basal metabolism", "Active metabolism", "SDA", "Excretion", "Available energy"),
               names_to = "Process", values_to = "value")

fg_long8 <- alloc8 %>%
  select(scenario, mass, f, g) %>%
  pivot_longer(cols = c(f, g), names_to = "Limiter", values_to = "value")

ggplot() +
  geom_area(data = alloc_long8, aes(mass, value, fill = Process), position = "stack", alpha = 0.9) +
  geom_line(data = fg_long8, aes(mass, value, colour = Limiter), linewidth = 0.8) +
  scale_x_log10(breaks = 10^c(-2, 0, 2, 4), labels = label_10pow(), expand = c(0, 0)) +
  scale_y_continuous(limits = c(0, 1), expand = c(0, 0)) +
  scale_fill_manual(values = c("Basal metabolism"="#440154", "Active metabolism"="#8a5796", SDA="#e0bce8", Excretion="gray90", "Available energy"="#67A5CA")) +
  scale_colour_manual(values = c(f = "#238b45", g = "#6a51a3")) +
  facet_wrap(~scenario, nrow = 2) +
  labs(x = "Body mass, w (g)", y = "Allocation / Cmax", colour = NULL,
       title = "Metabolic allocation scenarios with f and g") +
  th
```

# 10) Requested update: prey compensation pO2-v-T (4 panels)

```{r prey-compensation-pO2T, warning=FALSE}
d_comp_pi <- compute_state_surface(tr, masses = c(1e1, 1e5), Tseq = seq(0,30,by=0.25), pO2seq = pO2seq,
                                   preys = 0.75, prey_units = "prey_index", pair_mode = "cross", progress = TRUE)
d_comp_fl <- compute_state_surface(tr, masses = c(1e1, 1e5), Tseq = seq(0,30,by=0.25), pO2seq = pO2seq,
                                   preys = 0.75, prey_units = "feeding_level", pair_mode = "cross", progress = TRUE)

d_comp <- bind_rows(
  d_comp_pi %>% mutate(row_lab = "prey index = 0.75"),
  d_comp_fl %>% mutate(row_lab = "feeding level = 0.75")
) %>%
  add_masks() %>%
  mutate(
    mass_lab = factor(mass, levels = c(1e1, 1e5), labels = c("w = 10^1 g", "w = 10^5 g")),
    row_lab = factor(row_lab, levels = c("prey index = 0.75", "feeding level = 0.75"))
  )

plot_surface_masked(d_comp, x = "T", y = "pO2", z = "E_net_norm", palette = "blue",
                    fill_title = "Available energy", x_limits = c(0,30), y_limits = c(0,30),
                    contours = list(
                      contour_spec(z = "f", breaks = seq(0,1,0.2), colour = "#238b45", linewidth = 0.4, linetype = "solid"),
                      contour_spec(z = "g", breaks = seq(0,1,0.2), colour = "#6a51a3", linewidth = 0.4, linetype = "solid")
                    ),
                    contour_data = d_comp,
                    theme = th) +
  facet_grid2(rows = vars(row_lab), cols = vars(mass_lab)) +
  scale_x_continuous(breaks = c(0,10,20,30), limits = c(0,30), expand = c(0,0)) +
  scale_y_continuous(breaks = c(0,10,20,30), limits = c(0,30), expand = c(0,0)) +
  labs(x = "Temperature, T (°C)", y = expression("Ambient oxygen, " * p[O[2]*","*env] * " (kPa)"))
```


# 11) Added pO2_int surfaces for 4-panel combinations (purple)

```{r pO2int-4panel-updates, warning=FALSE}
# pO2 vs prey index (uses d_prey from section 2)
plot_surface_masked(d_prey, x="f_ref", y="pO2", z="pO2_int",
                    palette="purple", fill_title="pO2_int",
                    x_limits=c(0,1), y_limits=c(0,30),
                    contours=contour_spec(z="pO2_int", breaks=seq(0,30,5), linewidth=0.22, alpha=1),
                    theme=th) +
  facet_grid2(rows=vars(T_lab), cols=vars(mass_lab)) +
  scale_x_continuous(breaks = seq(0,1,0.2), labels = function(x) ifelse(x %in% c(0,1), as.character(as.integer(x)), sprintf("%.1f", x)), limits = c(0,1), expand = c(0,0)) +
  scale_y_continuous(breaks = c(0,10,20,30), limits = c(0,30), expand = c(0,0)) +
  labs(x = "prey index", y = expression("Ambient oxygen, " * p[O[2]*","*env] * " (kPa)"))

# pO2 vs temperature (feeding level configuration)
d_temp_fl_feed <- compute_state_surface(
  tr, masses=c(1e1,1e5), Tseq=seq(0,30,by=0.25), pO2seq=pO2seq,
  preys=c(0.9,0.6), prey_units="feeding_level", pair_mode="cross", progress=TRUE
) %>% add_masks() %>%
  mutate(mass_lab=factor(mass, levels=c(1e1,1e5), labels=c("w = 10^1 g","w = 10^5 g")),
         f_lab=factor(f_ref, levels=c(0.9,0.6), labels=c("feeding level = 0.9","feeding level = 0.6")))

plot_surface_masked(d_temp_fl_feed, x="T", y="pO2", z="pO2_int",
                    palette="purple", fill_title="pO2_int",
                    x_limits=c(0,30), y_limits=c(0,30),
                    contours=contour_spec(z="pO2_int", breaks=seq(0,30,5), linewidth=0.22, alpha=1),
                    theme=th) +
  facet_grid2(rows=vars(f_lab), cols=vars(mass_lab)) +
  scale_x_continuous(breaks = c(0,10,20,30), limits = c(0,30), expand = c(0,0)) +
  scale_y_continuous(breaks = c(0,10,20,30), limits = c(0,30), expand = c(0,0)) +
  labs(x = "Temperature, T (°C)", y = expression("Ambient oxygen, " * p[O[2]*","*env] * " (kPa)"))

# pO2 vs temperature (prey index configuration)
d_temp_fl_prey <- compute_state_surface(
  tr, masses=c(1e1,1e5), Tseq=seq(0,30,by=0.25), pO2seq=pO2seq,
  preys=c(0.9,0.6), prey_units="prey_index", D=2, pair_mode="cross", progress=TRUE
) %>% add_masks() %>%
  mutate(mass_lab=factor(mass, levels=c(1e1,1e5), labels=c("w = 10^1 g","w = 10^5 g")),
         f_lab=factor(f_ref, levels=c(0.9,0.6), labels=c("prey index = 0.9","prey index = 0.6")))

plot_surface_masked(d_temp_fl_prey, x="T", y="pO2", z="pO2_int",
                    palette="purple", fill_title="pO2_int",
                    x_limits=c(0,30), y_limits=c(0,30),
                    contours=contour_spec(z="pO2_int", breaks=seq(0,30,5), linewidth=0.22, alpha=1),
                    theme=th) +
  facet_grid2(rows=vars(f_lab), cols=vars(mass_lab)) +
  scale_x_continuous(breaks = c(0,10,20,30), limits = c(0,30), expand = c(0,0)) +
  scale_y_continuous(breaks = c(0,10,20,30), limits = c(0,30), expand = c(0,0)) +
  labs(x = "Temperature, T (°C)", y = expression("Ambient oxygen, " * p[O[2]*","*env] * " (kPa)"))
```
